---
title: "Geographic Visualization of Gun Violence in the U.S."
author: "Bich Ngoc Nguyen, Felix Ung, Anna Voloshina, Delaney Wu"
date: "1/12/2022"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=F, warning=F, include=F}
source("../source/summary.R")
source("../source/table.R")
source("../source/chart_1.R")
```

## Summary
The data set we found contain data collected from 2017 to 2018. A total of `r num_observations` incidences were recorded during this time period. Of those incidences, a total of `r total_deaths` deaths were recorded as a result of gun violence. Across all the state within the United States (including District of Columbia), `r max_state_deaths` had the most total deaths and `r min_state_deaths` had the least total deaths within that time span. The city with the most deaths during the data collection process was `r max_city_deaths`. 


## Table
### Table of Summary 
```{r table, echo=FALSE, message=F, warning=F}
library(knitr)
library(kableExtra)
kable(summary_table_verticle, format = "html") %>%
  kable_styling("striped", full_width = F, position = "center")  
```



## Charts
### Visualization of Total Gun Violence Incidence (2013-2018)

```{r chart_1, echo=FALSE}
plot(state_bar_chart)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
